The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2015-12-24 article.tex
Migrated the authors

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={???}
]{\inits{JWM}\fnm{John W} \snm{May}}

\address[id=um]{%                           % unique id
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},                     %
  \postcode{NL-6200 MD}                                % post or zip code
  \city{Maastricht},                              % city
  \cny{NL}                                    % country
}
\address[id=aff2]{%
  \orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  %\city{Kiel},
  \cny{UK}
}

% \author{
%   Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
%   \email{Egon L Willighagen - }
% \and
%   John May$^2$% // FIXED SECOND AUTHOR
%   \email{John May - COMPLETE@ebi.ac.uk}
% \and
%   Jonathan Alvarsson$^3$%
%   \email{Jonathan Alvarsson - COMPLETE}
% \and
%   Arvid Berg$^3$%
%   \email{Arvid Berg - COMPLETE}
% \and
%   Nina Jeliazkova$^4$%
%   \email{Nina Jeliakvova - COMPLETE}
% \and
%   Dazhi Jiao$^5$%
%   \email{Dazhi Jiao - COMPLETE}
% \and
%   Syed Asad Rahman$^6$%
%   \email{Syed Asad Rahman - COMPLETE}
% \and
%   Mark Rijnbeek$^2$%
%   \email{Mark Rijnbeek - COMPLETE}
% \and
%   Miguel Rojas Cherto$^7$%
%   \email{Miguel Rojas Cherto - COMPLETE}
% \and
%   Ola Spjuth$^3$%
%   \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
% \and
%   Gilleain Torrance$^5$%
%   \email{Gilleain Torrance - COMPLETE}
% \and
%   Rajarshi Guha$^{8}$% // FIXED ONE BUT LAST AUTHOR
%   \email{Rajarshi Guha - COMPLETE}
% \and
%   Christoph Steinbeck$^{2}$% // FIXED LAST AUTHOR
%   \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
% }
%      
% \address{
%     \iid(1) \\
%     \iid(2)Chemoinformatics and Metabolism team, European Bioinformatics Institute, Hinxton, UK, \\
%     \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, 751 24 Uppsala, Sweden \\
%     \iid(4)Ideaconsult Ltd, A. Kanchev 4, Sofia 1000, Bulgaria \\
%     \iid(5)Example Ltd., Glasgow, UK \\
%     \iid(6)Example Ltd., Glasgow, UK \\
%     \iid(7)Division of Analytical Biosciences, Leiden/Amsterdam Center for Drug Research, Leiden, The Netherlands \\
%     \iid(8)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA
% }

>>>>

\author[
   addressref={um},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={egon.willighagen@maastrichtuniversity.nl}   % email address
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={aff2},
   email={???}
]{\inits{JWM}\fnm{John W} \snm{May}}
\author[
   addressref={uppsala},
   email={}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={idea},
   email={}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={???},
   email={}
]{\inits{MRJ}\fnm{Miguel} \snm{Rojas-Cherto}}
\author[
   addressref={uppsala},
   email={}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={nih},
   email={}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={}
]{\inits{CS}\fnm{Christoph} \snm{Steinbeck}}

\address[id=um]{
  \orgname{Dept of Bioinformatics - BiGCaT, NUTRIM, Maastricht University}, % university, etc
  %\street{Waterloo Road},                     %
  \postcode{NL-6200 MD},
  \city{Maastricht},                              % city
  \cny{The Netherlands}                                    % country
}
\address[id=aff2]{
  \orgname{??},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105},
  %\city{Kiel},
  \cny{UK}
}
\address[id=uppsala]{
  \orgname{Department of Pharmaceutical Biosciences, Uppsala University},
  %\street{D\"{u}sternbrooker Weg 20},
  \postcode{751 24},
  \city{Uppsala},
  \cny{Sweden}
}
\address[id=idea]{
  \orgname{Ideaconsult Ltd},
  \street{A. Kanchev 4},
  \postcode{1000},
  \city{Sofia},
  \cny{Bulgaria}
}
\address[id=nih]{
  \orgname{NIH Center for Translational Therapeutics},
  \street{9800 Medical Center Drive},
  \postcode{MD 20878},
  \city{Rockville},
  \cny{USA}
}
\address[id=ebi]{
  \orgname{Chemoinformatics and Metabolism team, European Bioinformatics Institute},
  %\street{A. Kanchev 4},
  %\postcode{1000},
  \city{Hinxton},
  \cny{UK}
}
